A Polls-of-Polls Forecast for the 2024 United States Presidential Election Through Generalized Linear Model

### 2024-11-04 paper/paper.qmd
paper update

```
\newpage
```{r}
#| echo: false
#| fig-width: 5
#| fig-height: 5
#| fig-align: center

@@

```{r}
#| label: tbl-state-missing
#| tbl-cap: Summary of missing and total dates across key states
#| echo: false
#| message: false
#| warning: false
#| label: fig-state-comparison
#| fig-cap: State-by-State comparison of predicted percentages over time
#| fig-align: center

state_data <- prediction %>% filter(national_poll == 0)

@@

# Display the summary statistics in a nicely formatted table
missing_data_summary %>%
  kable() %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"), full_width = F)

```{r}
#| label: fig-state-comparison
#| fig-cap: State-by-State comparison of predicted percentages over time
#| echo: false
#| message: false
#| fig-align: center

@@

```{r}
#| label: fig-state-summary
#| fig-cap: Summary of Kamala Harris' predicted popular vote by key states
#| echo: false
#| message: false
#| fig-align: center
# Filter to keep only the most recent entry for each state based on 'end_date'
filtered_data <- prediction %>%
  filter(!is.na(state)) %>%
  arrange(state, end_date) %>%
  group_by(state) %>%
  slice_tail(n = 1) %>%
  ungroup() %>%
  select(state, end_date, predicted_pct)

>>>>

```
\newpage
```{r}
#| echo: false
#| message: false
#| warning: false
#| label: fig-populationtype
#| fig-cap: Distribution of population type
#| fig-width: 5
#| fig-height: 5
#| fig-align: center

@@

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: fig-state-comparison
#| fig-cap: State-by-State comparison of predicted percentages over time
#| fig-align: center
#| 
state_data <- prediction %>% filter(national_poll == 0)

@@

@@

```{r}
#| echo: false
#| message: false
#| warning: false
#| label: fig-state-summary
#| fig-cap: Summary of Kamala Harris' predicted popular vote by key states
#| fig-align: center
# Filter to keep only the most recent entry for each state based on 'end_date'
filtered_data <- prediction %>%
  filter(!is.na(state)) %>%
  arrange(state, end_date) %>%
  group_by(state) %>%
  slice_tail(n = 1) %>%
  ungroup() %>%
  select(state, end_date, predicted_pct)
